MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-13 docs/paper/out/paper.tex
reorganize Discussion, add sections -- paper

\subsection{Other}\label{other}

@@

\subsection{Novelty points of MG7}\label{novelty-points-of-mg7}

The most innovative ideas and developments integrated in MG7 are:

­- The management dependencies checking their correctness before
compilation using Scala type system - The automation of cloud resources
and processes (parallelization management) - The cloud-oriented
development of the system including a modeling AWS resources based on
the powerful data typing of Scala - The use of the Graph databases
paradigm to store and manage the taxonomy tree to obtain the taxonomic
assignments and the cumulative frequencies - MG7 provides a sustainable
model for updating the database of reference sequences appropriate to
face the challenging amount of sequences that are generating the new
high throughput technologies of sequencing

\subsection{Designed for future
challenges}\label{designed-for-future-challenges}

>>>>

@@

\subsection{What MG7 brings}\label{what-mg7-brings}

We could summarize the most innovative ideas and developments in MG7:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Treat data analysis as a software project. This makes for radical
  improvements in \emph{reproducibility}, \emph{reuse},
  \emph{versioning}, \emph{safety}, \emph{automation} and
  \emph{expressiveness}
\item
  input and output data, their locations and type are expressible and
  checked at compile-time using our Scala library \emph{datasets} ­3.
  management of dependencies and machine configurations using our Scala
  library \emph{Statika}
\item
  automation of AWS cloud resources and processes, including
  distribution and parallelization through the use of \emph{Loquat}
\item
  taxonomic data and related operations are treated natively as what
  they are: graphs, through the use of \emph{Bio4j}
\item
  MG7 provides a sustainable model for taxonomic assignment, appropriate
  to face the challenging amount of data that high throughput sequencing
  technologies generate
\end{enumerate}

\subsection{A new approach to data
analysis}\label{a-new-approach-to-data-analysis}

\subsection{Inputs, outputs, data: compile-time, expressive,
composable}\label{inputs-outputs-data-compile-time-expressive-composable}

\subsection{Tools, data, dependencies and machine
configurations}\label{tools-data-dependencies-and-machine-configurations}

\subsection{Parallel cloud execution ??}\label{parallel-cloud-execution}

\subsection{Taxonomy and Bio4j}\label{taxonomy-and-bio4j}

\subsection{Future-proof}\label{future-proof}
